Untitled

### 2025-03-14 script/r/discontinuity.Rmd
clean and maj

ggplot() +
  geom_sf(data = murdock_sf, aes (color="Murdock"), fill = "transparent", size = 1) + # Murdock map in black
  geom_sf(data = buffer, aes(color = "boundaries"), lwd = 1) + # 25km buffer around borders in red
  scale_color_manual(
    values = c("Murdock" = "black", "boundaries" = "red"),
    labels = c("25km boundaries", "Historical Ethnic Areas"),
    name = NULL 
  ) +
  theme_minimal(base_size = 15) +
  theme(
    panel.grid.major = element_blank(),  
    panel.grid.minor = element_blank(),  
    panel.background = element_blank(),   
    axis.text = element_blank(),         
    axis.ticks = element_blank(),         
    axis.title = element_blank(),         
    legend.key = element_rect(fill = "transparent", color = NA),
    legend.text = element_text(size = 8),
    legend.position = c(0.25, 0.35)
  )

ggsave("C:/Users/Redha CHABA/Documents/wp_git/rbci/plots/discontinuity/murdock_boundaries_map.jpg", width = 10, height = 6, dpi = 300)
```

@@

    # Plot the intersection geometry
    plot(inter_country$geometry, main = paste(country, "-", dist / 1000, "km buffer"))
  }
}

```

@@

ggsave("buffer_25.jpg", width = 10, height = 6, dpi = 300)

```

```{r}
data_trust_test <- readRDS("data/data_rds/data_27_02_25.rds")
data_trust_test%<>%
  ungroup()

@@

data_trust_test %<>%
  filter(spl==1)%>%
  left_join(bdd_geo, by = "id_unique") %>%
  select(-...1) %>%
  mutate(
    distance_border_km = distance_border / 1000,
    distance_border_km2 = distance_border_km^2,
    distance_border_km3 = distance_border_km^3
  )

@@

data_trust_test_sf <- st_as_sf(data_trust_test, coords = c("longitude", "latitude"), crs = st_crs(border_sample_50_union))

@@

# Filter data
filtered_data_list <- filter_by_border(data_trust_test_sf, borders)

@@

```

@@

# Prepare data
individuals <- data_trust_test %>%
  select(longitude, latitude, iso) %>%
  na.omit()

capitals <- data_trust_test %>%
  distinct(caplong, caplat, iso)%>%
  na.omit() %>%
  rename(longitude = caplong, latitude = caplat)

@@

ggsave("plots/map/obs_map.jpg", width = 10, height = 10, units = "in", dpi = 300)
```

>>>>

ggplot() +
  geom_sf(data = murdock_sf, aes (color="Murdock"), fill = "transparent", size = 1) +
  geom_sf(data = buffer, aes(color = "boundaries"), lwd = 1) +
  scale_color_manual(
    values = c("Murdock" = "black", "boundaries" = "red"),
    labels = c("25km boundaries", "Historical Ethnic Areas"),
    name = NULL 
  ) +
  theme_minimal(base_size = 15) +
  theme(
    panel.grid.major = element_blank(),  
    panel.grid.minor = element_blank(),  
    panel.background = element_blank(),   
    axis.text = element_blank(),         
    axis.ticks = element_blank(),         
    axis.title = element_blank(),         
    legend.key = element_rect(fill = "transparent", color = NA),
    legend.text = element_text(size = 8),
    legend.position = c(0.25, 0.35)
  )

ggsave("C:/Users/Redha CHABA/Documents/wp_git/rbci/plots/discontinuity/murdock_boundaries.jpg", width = 10, height = 6, dpi = 300)
```

@@

    # Plot the intersection geometry
    plot(inter_country$geometry, main = paste(country, "-", dist / 1000, "km buffer"))
  }
}
```

@@

ggsave("C:/Users/Redha CHABA/Documents/wp_git/rbci/plots/discontinuity/murdock_boundaries_inter.jpg", width = 10, height = 6, dpi = 300)
```

```{r}
data <- readRDS("data/data_rds/data_27_02_25.rds")
data%<>%
  ungroup()

@@

data %<>%
  filter(spl==1)%>%
  left_join(bdd_geo, by = "id_unique") %>%
  select(-...1) %>%
  mutate(
    distance_border_km = distance_border / 1000,
    distance_border_km2 = distance_border_km^2,
    distance_border_km3 = distance_border_km^3
  )

@@

data_sf <- st_as_sf(data, coords = c("longitude", "latitude"), crs = st_crs(border_sample_50_union))

@@

# Filter data
filtered_data_list <- filter_by_border(data_sf, borders)

@@

ggsave("C:/Users/Redha CHABA/Documents/wp_git/rbci/plots/discontinuity/murdock_boundaries_inter_spl.jpg", width = 10, height = 6, dpi = 300)
```

@@

# Prepare data
individuals <- data %>%
  select(longitude, latitude, iso) %>%
  na.omit()

capitals <- data %>%
  distinct(caplong, caplat, iso)%>%
  na.omit() %>%
  rename(longitude = caplong, latitude = caplat)

@@

ggsave("C:/Users/Redha CHABA/Documents/wp_git/rbci/plots/discontinuity/cty_spl.jpg", width = 10, height = 6, dpi = 300)
```

```{r}
selected_countries <- countries %>% 
 filter(iso_a3 %in% c("BEN", "NER"))

selected_capitals <- capitals %>%
 filter(iso%in% c("BEN", "NER"))

selected_murdock <- murdock_sf%>%
  filter(NAME=="DENDI")

ggplot() +
   geom_sf(data = selected_countries, fill = "white", color = "black") +
geom_sf(data = selected_murdock, fill = "green", color = "darkgreen", size = 1, alpha=0.5) +
 theme_void() + 
geom_point(data = selected_capitals, 
          aes(x = longitude, y = latitude, color = "Capitals"), 
         size = 2, shape = 22, fill = "red", show.legend = FALSE) +

geom_label(aes(x = 2.5, y = 10, label = "Benin"), color = "black", size = 6, fill = "lightgrey", label.size = 0.5) +
     geom_label(aes(x = 4, y = 14.5, label = "Niger"), color = "black", size = 6, fill = "lightgrey", label.size = 0.5) +

geom_text(aes(x = 2.4, y = 13.75, label = "Niamey"), color = "black", size = 5) +
geom_text(aes(x = 2.2, y = 6.6, label = "Porto-Novo"), color = "black", size = 5) +

  labs(color = NULL) +
   coord_sf(xlim = c(0, 5), ylim = c(6, 18), expand = FALSE)

ggsave("C:/Users/Redha CHABA/Documents/wp_git/rbci/plots/discontinuity/benin_niger.jpg", width = 10, height = 10, dpi = 300)
```
